---
title: "This report Child Health and Development Study"
subtitle: "Fork of original"
author: "Isabella Gollini"
date: today
format: 
  html:
    code-fold: true 
execute:
  echo: true
---

```{r}
#| label: setup
#| include: false
# so that code is not shown in report  
# load packages here to make dependencies clear
library(rio)
library(dplyr)
library(ggplot2)
```

# Version Control with GitHub

## Introduction

This report analyses data from a Child Health and Development Study 
conducted in the US 1960-1967.

```{r}
#| label: import-data
# add code here to import infant.xlsx
infant <- import("infant.xlsx", setclass = "tibble")
```

The data are a subset of the full study corresponding to live births of a 
single male foetus. Here we will focus on characteristics of the mother 
and child.

```{r}
#| label: explore-data
# add code here to import infant.xlsx
skimr::skim(infant)
```

```{r}
#| label: select-variables
# remove redundant variables and variables related to father
infant <- select(infant, -pluralty, -outcome, -sex, -(drace:dwt))
```

We exclude extremely premature babies (gestation less than 28 
weeks) and extremely late babies (gestation more than 52 weeks) from the 
analysis to focus on the typical gestation range.

```{r}
#| label: filter-variables
# remove redundant variables and variables related to father
infant <- filter(infant, gestation > 28 *7 & gestation < 52 * 7)
```

```{r}
#| label: mutate-variables
# if `ht` is 999, replace it with NA
infant <- mutate(infant, 
                 ht = ifelse(ht == 999, NA, ht))
```

```{r}
#| label: additional-processing
# processing of other variables ready for later analysis
infant <- infant |>
    mutate(gestation = ifelse(gestation == 999, NA, gestation))

```

## Low Birth Weight 

An infant is categorised as low weight if its birth weight is ≤ 2500 
grams, regardless of gestation. The following table shows the distribution 
of birth weight in the sample

```{r}
#| label: table-bwt
tab <- infant |>
    mutate(bwt = bwt * 28.35,
           `Birth weight (g)` = cut(bwt, 
                                    c(1500, 2000, 2500, 3000, 3500, 5000),
                                    dig.lab = 4)) |>
    group_by(`Birth weight (g)`) |>
    summarise(N = n())
knitr::kable(tab, align = "lr")
```

```{r} 
#| label: plots-bwt
#| layout-ncol: 2
#| fig-width: 4
#| fig-height: 4
#| fig-cap: 
#|   - "`ggplot` histogram"
#|   - "`ggplot` density curve"
ggplot(infant, aes(x = bwt * 28.35)) + 
  geom_histogram(bins = 20)
ggplot(infant, aes(x = bwt * 28.35)) + 
  geom_density()
```
